### 2023-01-31 Strydom_et_al_2023_graph_embedding_draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@056496e780c73ebc88e57c6540b8eb43cd84cf64 🚀

Treating interactions as probabilistic (as opposed to binary) events is
a more nuanced and realistic way to represent them. Dallas et al. (2017)
suggested that most interactions (links) in ecological networks are
cryptic, \emph{i.e.} uncommon or hard to observe. This argument echoes
Jordano (2016): sampling ecological interactions is difficult because it
requires first the joint observation of two species, and then the
observation of their interaction. In addition, it is generally expected
that weak or rare interactions will be more prevalent in networks than
common or strong interactions (Csermely, 2004), compared to strong,
persistent interactions; this is notably the case in food chains,
wherein many weaker interactions are key to the stability of a system
(Neutel et al., 2002). In the light of these observations, we expect to
see an over-representation of low-probability (hereafter rare)
interactions under a model that accurately predicts interaction
probabilities. Although defining an interaction as `rare' is perhaps not
as straight forward as one may assume (rare in the context of likelihood
of occurrence or the context of biologically plausible?) but for the
context of the discussion in this manuscript the core idea is that
construction of probabilistic networks affords us the nuance of
capturing this inherit variability of interaction occurrence.

Critically, the original metaweb definition, and indeed most past uses
of metawebs, was based on the presence/absence of interactions. Moving
towards \emph{probabilistic} metawebs, by representing interactions as
Bernoulli events (see \emph{e.g.} Poisot et al., 2016), offers the
opportunity to weigh these rare interactions appropriately. The inherent
plasticity of interactions is important to capture: there have been
documented instances of food webs undergoing rapid collapse/recovery
cycles over short periods of time (\emph{e.g.} Pedersen et al., 2017).
Furthermore, because the structure of the metaweb cannot be known in
advance, it is important to rely on predictive tools that do not assume
a specific network topology for link prediction (Gaucher et al., 2021),
but are able to work on generalizations of the network. These
considerations emphasize why metaweb predictions should focus on
quantitative (preferentially probabilistic) predictions, and this should
constrain the suite of models that are appropriate for prediction.

>>>>

Treating interactions as probabilistic (as opposed to binary) events is
a more nuanced and realistic way to represent them. Dallas et al. (2017)
suggested that most interactions (links) in ecological networks are
cryptic, \emph{i.e.} uncommon or hard to observe. This argument echoes
Jordano (2016): sampling ecological interactions is difficult because it
requires first the joint observation of two species, and then the
observation of their interaction. In addition, it is generally expected
that weak or rare interactions will be more prevalent in networks than
common or strong interactions (Csermely, 2004), compared to strong,
persistent interactions; this is notably the case in food chains,
wherein many weaker interactions are key to the stability of a system
(Neutel et al., 2002). In the light of these observations, we expect to
see an over-representation of low-probability (hereafter rare)
interactions under a model that accurately predicts interaction
probabilities.

Yet, the original metaweb definition, and indeed most past uses of
metawebs, was based on the presence/absence of interactions. Moving
towards \emph{probabilistic} metawebs, by representing interactions as
Bernoulli events (see \emph{e.g.} Poisot et al., 2016), offers the
opportunity to weigh these rare interactions appropriately. The inherent
plasticity of interactions is important to capture: there have been
documented instances of food webs undergoing rapid collapse/recovery
cycles over short periods of time (\emph{e.g.} Pedersen et al., 2017).
Furthermore, because the structure of the metaweb cannot be known in
advance, it is important to rely on predictive tools that do not assume
a specific network topology for link prediction (Gaucher et al., 2021),
but are able to work on generalizations of the network. These
considerations emphasize why metaweb predictions should focus on
quantitative (preferentially probabilistic) predictions, and this should
constrain the suite of models that are appropriate for prediction.
